The Leaky Semicolon (Supplementary Material)

### 2021-11-12 paper/outro.tex
typo in 10

We have defined the soundness of compiler optimizations in the model, rather
than contextually: $\aCmd'$ is a sound refinement of $\aCmd$ if
$\sem{\aCmd'}\subseteq\sem{\aCmd}$.  This approach has several
advantages---for example, it is immediate that a sound optimization is sound
in any context.  It also has a disadvantage: some optimizations complicate
the semantics.  For example, \PwTmca{} does not validate access elimination,
such as store-forwarding and dead-write-removal---consider that complete
executions of
\begin{math}
  \sem{\PW{x}{1}\SEMI\PR{x}{r}}
\end{math}
must include a read action and that complete executions of
\begin{math}
  \sem{\PW{x}{1}\SEMI\PW{x}{2}}
\end{math}
must include two write actions.  As another example, \PwTmca{} does not
validate the reverse inclusions for
\reflem{lem:if}\ref{lem:ifelse:if:if}---consider that
\begin{math}
  \sem{\IF{r}
  \THEN \PW{x}{1}
  \ELSE \PW{x}{2}
  \FI}
\end{math}
has an augmented (\reflem{lem:augment}) execution with
\begin{math}
  (r{=}0\mid\DW{x}{2})
  \xwki
  (r{\neq}0\mid\DW{x}{1}),
\end{math}
whereas
\begin{math}
  \sem{
    \IF{r} \THEN \PW{x}{1}\FI
    \SEMI
    \IF{\BANG r} \THEN \PW{x}{2}\FI
  \FI}
\end{math}
has no such execution.  We expect that these optimizations can be validated,
at the cost of complicating the semantics.  For access elimination, it is
likely sufficient to allow events with different actions to merge.  For
\reflem{lem:if}\ref{lem:ifelse:if:if}, it is likely sufficient to encoding
$\rdelay$ in the logic---the problem in the execution above is that $\rdelay$
introduces order regardless of whether preconditions are disjoint.
%\todo{Comment on \PwTpo{} and \PwTc{}?}

>>>>

We have defined the soundness of compiler optimizations in the model, rather
than contextually: $\aCmd'$ is a sound refinement of $\aCmd$ if
$\sem{\aCmd'}\subseteq\sem{\aCmd}$.  This approach has several
advantages---for example, it is immediate that a sound optimization is sound
in any context.  It also has a disadvantage: some optimizations complicate
the semantics.  For example, \PwTmca{} does not validate access elimination,
such as store-forwarding and dead-write-removal---consider that complete
executions of
\begin{math}
  \sem{\PW{x}{1}\SEMI\PR{x}{r}}
\end{math}
must include a read action and that complete executions of
\begin{math}
  \sem{\PW{x}{1}\SEMI\PW{x}{2}}
\end{math}
must include two write actions.  As another example, \PwTmca{} does not
validate the reverse inclusions for
\reflem{lem:if}\ref{lem:ifelse:if:if}---consider that
\begin{math}
  \sem{\IF{r}
  \THEN \PW{x}{1}
  \ELSE \PW{x}{2}
  \FI}
\end{math}
has an augmented (\reflem{lem:augment}) execution with
\begin{math}
  (r{=}0\mid\DW{x}{2})
  \xwki
  (r{\neq}0\mid\DW{x}{1}),
\end{math}
whereas
\begin{math}
  \sem{
    \IF{r} \THEN \PW{x}{1}\FI
    \SEMI
    \IF{\BANG r} \THEN \PW{x}{2}\FI
  \FI}
\end{math}
has no such execution.  We expect that these optimizations can be validated,
at the cost of complicating the semantics.  For access elimination, it is
likely sufficient to allow events with different actions to merge.  For
\reflem{lem:if}\ref{lem:ifelse:if:if}, it is likely sufficient to encode
$\rdelay$ in the logic---the problem in the execution above is that $\rdelay$
introduces order even when the preconditions are disjoint.
%\todo{Comment on \PwTpo{} and \PwTc{}?}
